Tissue Enrichment Analysis (TEA)

### 2016-04-19 tests/hgf_benchmarking/doc/SI/FolderStructure.tex

Files are titled according to a common schema. For example, the file \\
\texttt{WBPaper00013489\_Ray\_Enriched\_WBbt\_0006941\_25.csv}\\
refers to the \textbf{WormBase Paper 0013489}, which should be `\textbf{Ray Enriched}', and specifically should be enriched in term `\textbf{WBbt:0006941}'. The gene set that was used for this analysis is contained in the SI folder named `\textbf{golden gene sets}' and is contained in a homologously named csv file.

@@

Alternatively, when comparing two dictionaries, the nomenclature is:
neuronal\_comparison\_GABAergic\_33-50_WBPaper0037950_complete.csv
Which refers to a `GABAergic neuronal' lists, comparing dictionaries with cutoffs of 33-50 (all other parameters are the same) using paper 37950.

@@

\subsection*{test_list_efaecalis.txt}

>>>>

Files are titled according to a common schema. For example, the file \\
\texttt{WBPaper00013489\_Ray\_Enriched\_WBbt\_0006941\_25.csv}\\
refers to the \textbf{WormBase Paper 0013489}, which should be enriched in `\textbf{Ray Enriched (WBbt:0006941)}' and contains \textbf{25} genes. The gene set that was used for this analysis is contained in the SI folder named `\textbf{golden gene sets}' and is contained in a homologously named csv file.

@@

Alternatively, when comparing two dictionaries, the nomenclature is:
neuronal\_comparison\_GABAergic\_33-50\_WBPaper0037950\_complete.csv
Which refers to a `GABAergic neuronal' lists, comparing dictionaries with cutoffs of 33-50 (all other parameters are the same) using paper 37950.

@@

\subsection*{test\_list\_efaecalis.txt}
